Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-07-30 paper.tex

Figure~\ref{fig:results-real-als} shows the accuracy results for ALS without bias. Among the methods that performed 
well in the synthetic dataset, RFNU performs the best, with an accuracy 
higher than 0.95 for all datasets, when the training ratio is larger 
than 0.5. RS and RFNTL are slightly underperforming compared to RFNU. 
Complete rows and complete columns do not even reach the accuracy of 
the dummy classifier. The reference method, Random Unreal, has an 
accuracy close to 1, which shows that collaborative filtering works 
well on this dataset too.
\todo{why is the performance of columns so variable?}

@@

Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
The PreFreesurfer dataset is not included since specificity of RFNTL, 
RFNU, RS and complete rows is undefined at this training ratio (the 
test set only contains positive elements \todo{check matrix with 
Soudabeh to confirm}). The average sensitivity and specificity values 
are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
performing method on average.

@@

\subsection{Varying the number of factors}
Figure~\ref{fig:factors} shows the effect of the number of factors used 
in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
clear effect of the number of factors on the accuracy.
\begin{figure}[h]
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
\label{fig:factors}
\end{figure}

>>>>

Figure~\ref{fig:results-real-als} shows the accuracy results for ALS without bias. Among the methods that performed 
well in the synthetic dataset, RFNU performs the best, with an accuracy 
higher than 0.95 for all datasets, when the training ratio is larger 
than 0.5. RS and RFNTL are slightly underperforming compared to RFNU. 
Complete rows and complete columns do not even reach the accuracy of 
the dummy classifier. The reference method, Random Unreal, has an 
accuracy close to 1, which shows that collaborative filtering works 
well on this dataset too.

@@

Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
The PreFreesurfer dataset is not included since specificity of RFNTL, 
RFNU, RS and complete rows is undefined at this training ratio (the 
test set only contains positive elements \todo{Soudabeh: check matrix to confirm}). The average sensitivity and specificity values 
are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
performing method on average.

@@

\subsection{Varying the number of factors}
Figure~\ref{fig:factors} shows the effect of the number of factors used 
in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
clear effect of the number of factors on the accuracy. \todo{Soudabeh, add results for 50 and 800 factors}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
\label{fig:factors}
\end{figure}
